Modeling ice-shelf cavities and tabular icebergs using Lagrangian elements

### 2018-10-26 Lagrangian_MISOMIP.tex
Made paths to figures relative

 \begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Two_panel_schematic_shelf.png}
\caption{ {Schematic showing how ice shelves and tabular icebergs are constructed using Lagrangian elements. 
(a) Schematic of multiple ice elements that are joined together by numerical bonds (magenta lines) to form larger structures such as ice shelves and tabular icebergs. These numerical elements have finite extent and are able to interact with the ocean across multiple grid cells, and can interact with other elements. (b) Areal photograph of an ice shelf and tabular iceberg with elements superimposed over it to illustrate how the Lagrangian elements can be used to model ice shelves and tabular icebergs. In this schematic the ice elements (purple dots) are initialized in a staggered lattice covering the surface area of the iceberg. For the purpose of mass aggregation, the ice elements are assumed to have hexagonal shape (red hexagons). For the purpose of element interactions, the ice elements are assumed to be circular (black circles). Elements are initially bonded to adjacent elements using numerical bonds (magenta lines). These numerical bonds form equilateral triangles which give the shape rigidity. An ocean grid has been included (dashed cyan lines). 
\textcolor{red}{Still need to update this figure to include the super imposed hexagons. Also, perhaps we want to remove some of the text in the caption? (e.g.: remove from the words "In this schematic the ice elements").}
%The background photo in the larger schematic is an areal photograph of iceberg PIIB (Area= 42 $\textrm{km}^{2}$) taken in Baffin Bay in 2012. The red ship can be identified on the bottom of the photo for scale. 
%Schematic showing how Lagrangian elements are used when modeling tabular icebergs. Lagrangian elements (blue dots) are initialized in a staggered lattice covering the surface area of the iceberg. For purposed of mass aggregation, the ice elements are assumed to have hexagonal shape (grey hexagons). For purposed of element interactions, the ice elements are assumed to be circular (black circles). Elements are initially bonded to adjacent elements using numerical bonds (dashed white lines). These numerical bonds form equilateral triangles which give the shape rigidity. 
%The inset panel shows a schematic of the intersection of a hexagonal element and the ocean grid. The colors indicate the fraction of the hexagon that lies in each grid cell. These fractions are used as weights to spread iceberg model properties to the ocean grid (see text for more details).
}}
\end{center}
\label{fig:Schematic}
\end{figure}
 \clearpage

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/side_and_top_view_ALE_z_Mixed_Melt_Collapse_temp_layers_x12.png}
%\caption{ {Snapshots of a simulation where a Lagrangian ice-shelf calves a tabular iceberg viewed (a) from above and (b) from the side. The snapshots is taken 30 days after calving. Panel (a) shows the sea surface temperature. Grid cells with ice mass $>10^{4}$ kg are plotted in white, with grey shading indicating thinner ice. Panel (b) shows a vertical sections of ocean temperature at $x$=54~km. The position of the vertical section is shown by the dashed line in panel (a). The solid line in panel (a) shows the position of the grounding line.}}
%\end{center}
%\label{fig:Iceberg_calving}
%\end{figure}
% \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_temp_anomaly.png}
\caption{ {Snapshots of sea surface temperature anomalies in the iceberg-calving simulation. The anomalies are relative to pre-calving temperatures. Snapshots are taken (a) 7, (b) 15, and (c) 50 days after calving. Grid cells with ice mass $> 10^{4}$ kg are plotted in white, with grey shading indicating thinner ice.  The black and blue dashed line in panel (a) shows the location of the vertical transects shown in Figures \ref{fig:Temperature_section_Collapse_yz} and \ref{fig:v_velocity_vertical}, and \ref{fig:Temperature_section_Collapse_xz}, respectively.}}
\end{center}
%FIgure created by \end{center}
\label{fig:SST_snapshots}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_D_mass_spread_mass.png}
\caption{ {(a) Ocean bottom topography and (c) ice-shelf draft used to initialized the static ice shelf experiment simulation. The ice draft is calculated from the total mass of ice intersecting each ocean grid cell (see Section 2.6). Panel (b) shows the initial ice draft that would be calculated if the mass aggregation onto the Eularian grid was not used (i.e. elements treated as point masses). The lower and upper black lines denote the grounding line and ice shelf front, respectively. This figure is reproduced from \citep{Stern2017}. } \label{fig:ISOMIP_mass_and_topog}}
\end{center}
\end{figure}
 \clearpage

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Lagrangian_shelf_domain.png}
%\caption{ {Ocean bottom topography and ice-shelf draft used in the Lagrangian and Eulerian static ice-shelf simulations}}
%\end{center}
%\label{fig:ISOMIP_mass_and_topog}
%\end{figure}
% \clearpage

\begin{figure}
\begin{center}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_barotropic_sf.png}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_comparison_barotropic_sf.png}
\caption{ {Time-averaged barotropic stream function in the (a) Lagrangian and (b) Eulerian simulations in the static ice-shelf configuration. Panel (c) shows the difference between panels (a) and (b). The time averages are taken over 5 years of model time, beginning at the end of the 5 year spin up period. \textcolor{red}{Something is wrong with the units in this figure}}}
\end{center}
%FIgure created by \end{center}
\label{fig:Bt_comparison}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_barotropic_sf.png}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Diagrams/Iceberg_scehmatic_with_red.pdf}
\caption{ {{\small Schematic illustrating how the ocean hydrography is affected by iceberg calving. Cool and warm water anomalies are indicated in blue and red, respectively, and ocean currents are shown using arrows.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_temp_zold_x20_anomaly.png}
\caption{ {Snapshots of vertical sections of ocean temperature anomaly at $x$=40~km in the iceberg-calving experiment. The anomalies are relative to pre-calving temperatures. Snapshots are taken (a) 1, (b) 15, and (c) 50 days after calving. In each panel, the base of the ice before calving and at the time of the snapshot are shown by the solid and dashed black lines, respectively. Positions that were not the ocean interior at in both snapshots are masked in grey. The position of the vertical transects is shown by the black dashed lines in Figure \ref{fig:SST_snapshots}a.}}
\end{center}
%FIgure created by \end{center}
\label{fig:Temperature_section_Collapse_yz}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_temp_zold_x149_anomaly_mask.png}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_temp_zold_x149_anomaly.png}
\caption{ {Snapshots of vertical sections of ocean temperature anomaly at $y$=300~km in the tabular-iceberg-calving experiment. The anomalies are relative to pre-calving temperatures. Snapshots are taken (a) 1, (b) 15, and (c) 50 days after calving. The position of the vertical transects is shown by the blue dashed lines in Figure \ref{fig:SST_snapshots}a. }}
\end{center}
%FIgure created by \end{center}
\label{fig:Temperature_section_Collapse_xz}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_u.png}
\caption{ {Snapshots of ocean zonal velocity at $z$=197.5~m(?) in the iceberg-calving experiment. Snapshots are taken (a) 1, (b) 15, and (c) 50 days after calving. \textcolor{red}{I should include an outline of the iceberg shape in this figure}}}
\end{center}
%FIgure created by \end{center}
\label{fig:u_velocity_horizontal}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_solo_temp_u_v_calved.png}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_solo_u_cropped.png}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_temp_zold_x10_anomaly_mask.png}
\caption{ {Snapshots of vertical sections of ocean (a) zonal velocity, (b) meridional velocity,  and (c) temperature anomaly at $x$=60~km in the tabular-iceberg-calving experiment. The anomalies are relative to pre-calving temperatures. Snapshots are taken 50 days after calving. 
%The position of the vertical transects is shown by the dashed lines in Figure \ref{fig:SST_snapshots}c. 
\textcolor{red}{Should we add the position to Figure 2a?}}}
\end{center}
\label{fig:Taylor_column}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_v_z40_.png}
\caption{ {Snapshots of ocean meridional velocity at $z$=197.5~m in the iceberg-calving experiment. Snapshots are taken (a) 1, (b) 15, and (c) 50 days after calving. \textcolor{red}{I should include an outline of the iceberg shape in this figure}}}
\end{center}
%FIgure created by \end{center}
\label{fig:v_velocity_horizontal}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_melt_m_per_year_anomaly.png}
\caption{ { Snapshots of the melt rate anomaly, at the ice-shelf base in the tabular iceberg-calving simulation. The anomalies are relative to pre-calving melt rates.  Snapshots are taken (a) 7, (b) 15, and (c) 50 days after calving. }}
\end{center}
%FIgure created by \end{center}
\label{fig:Melt_rate_snapshots}
\end{figure}
 \clearpage

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_v_layers_x149_mask_t0_t1_t50.png}
%\caption{ {Snapshots of vertical sections of meridional velocity at $y$=300~km in the tabular-iceberg-calving experiment. Snapshots are taken (a) 0, (b) 1, and (c) 50 days after calving. The position of the vertical transects is shown by the blue dashed lines in Figure \ref{fig:SST_snapshots}a. \textcolor{red}{Could show 1,14 and 50 days after calving to be consistent with the other Figures. But this figure is more interesting}}}
%\end{center}
%\label{fig:meridional_velocity_snapshots}
%\end{figure}
% \clearpage

@@

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/fixed_drift_bond_Iceberg_calving.png}
%\caption{ {Need to update this Figure. Also, I should try using orientation with the Bonds.}}
%\end{center}
%FIgure created by \end{center}
%\label{fig:}
%\end{figure}

@@

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/fixed_drift_bond_salt_layers.png}
%\caption{ {}}
%\end{center}
%FIgure created by \end{center}
%\label{fig:}
%\end{figure}

@@

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_fixed_01_u_layers.png}
%\caption{ {Need to update this Figure. }}
%\end{center}
%FIgure created by \end{center}
%\label{fig:}
%\end{figure}

@@

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_fixed_01_v_layers.png}
%\caption{ {Need to update this Figure. }}
%\end{center}
%FIgure created by \end{center}
%\label{fig:}
%\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_comparison_melt.png}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_melt.png}
\caption{ {Time-averaged melt rates in the (a) Lagrangian and (b) Eulerian simulations in the static ice-shelf configuration. Panel (c) shows the difference between panels (a) and (b). The time averages are taken over 5 years of model time, beginning at the end of the 5 year spin up period.}}
\end{center}
\label{fig:Melt_comparison}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_comparison_salt_layers.png}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_salt_layers.png}
\caption{ {Time-averaged vertical sections of salinity at  $x$=40~km in the (a) Lagrangian and (b) Eulerian simulations in the static ice-shelf configuration. Panel (c) shows the difference between panels (a) and (b). The time averages are taken over 5 years of model time, beginning at the end of the 5 year spin up period. The position of the vertical transects is shown by the black dashed lines in Figure \ref{fig:SST_snapshots}a.
}}
\end{center}
\label{fig:Salt_comparison}
\end{figure}
 \clearpage

 \begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_solo_temp_v_v.png}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_temp_v_v.png}
\caption{ {Snapshots of the static ice-shelf experiment taken after 5 years of model simulation, using the Lagrangian ice-shelf model coupled to the MOM6 ocean model. Panels show cross sections of the (a) the steady-state ocean temperature, and (b) the meridional ocean velocity. Panel (c) again shows the meridional ocean velocity, and is zoomed into the region near the ice-shelf base (the zoomed-in region is indicated with a black box (b)).}}
\end{center}
\label{fig:static_solo_temp_v_v}
\end{figure} 
 \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
\caption{ {Results of the static ice-shelf experiment using the Lagrangian ice-shelf model coupled to MOM6. The three panels show 5 year time average of the (a) melt rate, (b) top-of-ocean temperature and (c) frictional velocity, $u^{*}$, at the base of the ice shelf. Fields are only shown in regions where the ice area fraction is $\geq 0.8$.}}
\end{center}
\label{fig:static_solo_melt}
\end{figure} 
 \clearpage

>>>>

 \begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{Figures/Two_panel_schematic_shelf.png}
\caption{ {Schematic showing how ice shelves and tabular icebergs are constructed using Lagrangian elements. 
(a) Schematic of multiple ice elements that are joined together by numerical bonds (magenta lines) to form larger structures such as ice shelves and tabular icebergs. These numerical elements have finite extent and are able to interact with the ocean across multiple grid cells, and can interact with other elements. (b) Areal photograph of an ice shelf and tabular iceberg with elements superimposed over it to illustrate how the Lagrangian elements can be used to model ice shelves and tabular icebergs. In this schematic the ice elements (purple dots) are initialized in a staggered lattice covering the surface area of the iceberg. For the purpose of mass aggregation, the ice elements are assumed to have hexagonal shape (red hexagons). For the purpose of element interactions, the ice elements are assumed to be circular (black circles). Elements are initially bonded to adjacent elements using numerical bonds (magenta lines). These numerical bonds form equilateral triangles which give the shape rigidity. An ocean grid has been included (dashed cyan lines). 
\textcolor{red}{Still need to update this figure to include the super imposed hexagons. Also, perhaps we want to remove some of the text in the caption? (e.g.: remove from the words "In this schematic the ice elements").}
%The background photo in the larger schematic is an areal photograph of iceberg PIIB (Area= 42 $\textrm{km}^{2}$) taken in Baffin Bay in 2012. The red ship can be identified on the bottom of the photo for scale. 
%Schematic showing how Lagrangian elements are used when modeling tabular icebergs. Lagrangian elements (blue dots) are initialized in a staggered lattice covering the surface area of the iceberg. For purposed of mass aggregation, the ice elements are assumed to have hexagonal shape (grey hexagons). For purposed of element interactions, the ice elements are assumed to be circular (black circles). Elements are initially bonded to adjacent elements using numerical bonds (dashed white lines). These numerical bonds form equilateral triangles which give the shape rigidity. 
%The inset panel shows a schematic of the intersection of a hexagonal element and the ocean grid. The colors indicate the fraction of the hexagon that lies in each grid cell. These fractions are used as weights to spread iceberg model properties to the ocean grid (see text for more details).
}}
\end{center}
\label{fig:Schematic}
\end{figure}
 \clearpage

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.99\textwidth]{Figures/side_and_top_view_ALE_z_Mixed_Melt_Collapse_temp_layers_x12.png}
%\caption{ {Snapshots of a simulation where a Lagrangian ice-shelf calves a tabular iceberg viewed (a) from above and (b) from the side. The snapshots is taken 30 days after calving. Panel (a) shows the sea surface temperature. Grid cells with ice mass $>10^{4}$ kg are plotted in white, with grey shading indicating thinner ice. Panel (b) shows a vertical sections of ocean temperature at $x$=54~km. The position of the vertical section is shown by the dashed line in panel (a). The solid line in panel (a) shows the position of the grounding line.}}
%\end{center}
%\label{fig:Iceberg_calving}
%\end{figure}
% \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Collapse_temp_anomaly.png}
\caption{ {Snapshots of sea surface temperature anomalies in the iceberg-calving simulation. The anomalies are relative to pre-calving temperatures. Snapshots are taken (a) 7, (b) 15, and (c) 50 days after calving. Grid cells with ice mass $> 10^{4}$ kg are plotted in white, with grey shading indicating thinner ice.  The black and blue dashed line in panel (a) shows the location of the vertical transects shown in Figures \ref{fig:Temperature_section_Collapse_yz} and \ref{fig:v_velocity_vertical}, and \ref{fig:Temperature_section_Collapse_xz}, respectively.}}
\end{center}
%FIgure created by \end{center}
\label{fig:SST_snapshots}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{Figures/ALE_z_static_shelf_solo_D_mass_spread_mass.png}
\caption{ {(a) Ocean bottom topography and (c) ice-shelf draft used to initialized the static ice shelf experiment simulation. The ice draft is calculated from the total mass of ice intersecting each ocean grid cell (see Section 2.6). Panel (b) shows the initial ice draft that would be calculated if the mass aggregation onto the Eularian grid was not used (i.e. elements treated as point masses). The lower and upper black lines denote the grounding line and ice shelf front, respectively. This figure is reproduced from \citep{Stern2017}. } \label{fig:ISOMIP_mass_and_topog}}
\end{center}
\end{figure}
 \clearpage

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.99\textwidth]{Figures/Lagrangian_shelf_domain.png}
%\caption{ {Ocean bottom topography and ice-shelf draft used in the Lagrangian and Eulerian static ice-shelf simulations}}
%\end{center}
%\label{fig:ISOMIP_mass_and_topog}
%\end{figure}
% \clearpage

\begin{figure}
\begin{center}
%\includegraphics[width=0.99\textwidth]{Figures/ALE_z_static_shelf_comparison_barotropic_sf.png}
\includegraphics[width=0.99\textwidth]{Figures/Wind_static_shelf_comparison_barotropic_sf.png}
\caption{ {Time-averaged barotropic stream function in the (a) Lagrangian and (b) Eulerian simulations in the static ice-shelf configuration. Panel (c) shows the difference between panels (a) and (b). The time averages are taken over 5 years of model time, beginning at the end of the 5 year spin up period. \textcolor{red}{Something is wrong with the units in this figure}}}
\end{center}
%FIgure created by \end{center}
\label{fig:Bt_comparison}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
%\includegraphics[width=0.99\textwidth]{Figures/ALE_z_static_shelf_comparison_barotropic_sf.png}
\includegraphics[width=0.99\textwidth]{Diagrams/Iceberg_scehmatic_with_red.pdf}
\caption{ {{\small Schematic illustrating how the ocean hydrography is affected by iceberg calving. Cool and warm water anomalies are indicated in blue and red, respectively, and ocean currents are shown using arrows.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Collapse_temp_zold_x20_anomaly.png}
\caption{ {Snapshots of vertical sections of ocean temperature anomaly at $x$=40~km in the iceberg-calving experiment. The anomalies are relative to pre-calving temperatures. Snapshots are taken (a) 1, (b) 15, and (c) 50 days after calving. In each panel, the base of the ice before calving and at the time of the snapshot are shown by the solid and dashed black lines, respectively. Positions that were not the ocean interior at in both snapshots are masked in grey. The position of the vertical transects is shown by the black dashed lines in Figure \ref{fig:SST_snapshots}a.}}
\end{center}
%FIgure created by \end{center}
\label{fig:Temperature_section_Collapse_yz}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Collapse_temp_zold_x149_anomaly_mask.png}
%\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Collapse_temp_zold_x149_anomaly.png}
\caption{ {Snapshots of vertical sections of ocean temperature anomaly at $y$=300~km in the tabular-iceberg-calving experiment. The anomalies are relative to pre-calving temperatures. Snapshots are taken (a) 1, (b) 15, and (c) 50 days after calving. The position of the vertical transects is shown by the blue dashed lines in Figure \ref{fig:SST_snapshots}a. }}
\end{center}
%FIgure created by \end{center}
\label{fig:Temperature_section_Collapse_xz}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Collapse_u.png}
\caption{ {Snapshots of ocean zonal velocity at $z$=197.5~m(?) in the iceberg-calving experiment. Snapshots are taken (a) 1, (b) 15, and (c) 50 days after calving. \textcolor{red}{I should include an outline of the iceberg shape in this figure}}}
\end{center}
%FIgure created by \end{center}
\label{fig:u_velocity_horizontal}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
%\includegraphics[width=0.99\textwidth]{Figures/Wind_static_shelf_solo_temp_u_v_calved.png}
\includegraphics[width=0.99\textwidth]{Figures/Wind_static_shelf_solo_u_cropped.png}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Collapse_temp_zold_x10_anomaly_mask.png}
\caption{ {Snapshots of vertical sections of ocean (a) zonal velocity, (b) meridional velocity,  and (c) temperature anomaly at $x$=60~km in the tabular-iceberg-calving experiment. The anomalies are relative to pre-calving temperatures. Snapshots are taken 50 days after calving. 
%The position of the vertical transects is shown by the dashed lines in Figure \ref{fig:SST_snapshots}c. 
\textcolor{red}{Should we add the position to Figure 2a?}}}
\end{center}
\label{fig:Taylor_column}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Collapse_v_z40_.png}
\caption{ {Snapshots of ocean meridional velocity at $z$=197.5~m in the iceberg-calving experiment. Snapshots are taken (a) 1, (b) 15, and (c) 50 days after calving. \textcolor{red}{I should include an outline of the iceberg shape in this figure}}}
\end{center}
%FIgure created by \end{center}
\label{fig:v_velocity_horizontal}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Collapse_melt_m_per_year_anomaly.png}
\caption{ { Snapshots of the melt rate anomaly, at the ice-shelf base in the tabular iceberg-calving simulation. The anomalies are relative to pre-calving melt rates.  Snapshots are taken (a) 7, (b) 15, and (c) 50 days after calving. }}
\end{center}
%FIgure created by \end{center}
\label{fig:Melt_rate_snapshots}
\end{figure}
 \clearpage

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Collapse_v_layers_x149_mask_t0_t1_t50.png}
%\caption{ {Snapshots of vertical sections of meridional velocity at $y$=300~km in the tabular-iceberg-calving experiment. Snapshots are taken (a) 0, (b) 1, and (c) 50 days after calving. The position of the vertical transects is shown by the blue dashed lines in Figure \ref{fig:SST_snapshots}a. \textcolor{red}{Could show 1,14 and 50 days after calving to be consistent with the other Figures. But this figure is more interesting}}}
%\end{center}
%\label{fig:meridional_velocity_snapshots}
%\end{figure}
% \clearpage

@@

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.99\textwidth]{Figures/fixed_drift_bond_Iceberg_calving.png}
%\caption{ {Need to update this Figure. Also, I should try using orientation with the Bonds.}}
%\end{center}
%FIgure created by \end{center}
%\label{fig:}
%\end{figure}

@@

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.99\textwidth]{Figures/fixed_drift_bond_salt_layers.png}
%\caption{ {}}
%\end{center}
%FIgure created by \end{center}
%\label{fig:}
%\end{figure}

@@

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.99\textwidth]{Figures/snapshots_fixed_01_u_layers.png}
%\caption{ {Need to update this Figure. }}
%\end{center}
%FIgure created by \end{center}
%\label{fig:}
%\end{figure}

@@

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.99\textwidth]{Figures/snapshots_fixed_01_v_layers.png}
%\caption{ {Need to update this Figure. }}
%\end{center}
%FIgure created by \end{center}
%\label{fig:}
%\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{Figures/Wind_static_shelf_comparison_melt.png}
%\includegraphics[width=0.99\textwidth]{Figures/ALE_z_static_shelf_comparison_melt.png}
\caption{ {Time-averaged melt rates in the (a) Lagrangian and (b) Eulerian simulations in the static ice-shelf configuration. Panel (c) shows the difference between panels (a) and (b). The time averages are taken over 5 years of model time, beginning at the end of the 5 year spin up period.}}
\end{center}
\label{fig:Melt_comparison}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{Figures/Wind_static_shelf_comparison_salt_layers.png}
%\includegraphics[width=0.99\textwidth]{Figures/ALE_z_static_shelf_comparison_salt_layers.png}
\caption{ {Time-averaged vertical sections of salinity at  $x$=40~km in the (a) Lagrangian and (b) Eulerian simulations in the static ice-shelf configuration. Panel (c) shows the difference between panels (a) and (b). The time averages are taken over 5 years of model time, beginning at the end of the 5 year spin up period. The position of the vertical transects is shown by the black dashed lines in Figure \ref{fig:SST_snapshots}a.
}}
\end{center}
\label{fig:Salt_comparison}
\end{figure}
 \clearpage

 \begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{Figures/Wind_static_shelf_solo_temp_v_v.png}
%\includegraphics[width=0.99\textwidth]{Figures/ALE_z_static_shelf_solo_temp_v_v.png}
\caption{ {Snapshots of the static ice-shelf experiment taken after 5 years of model simulation, using the Lagrangian ice-shelf model coupled to the MOM6 ocean model. Panels show cross sections of the (a) the steady-state ocean temperature, and (b) the meridional ocean velocity. Panel (c) again shows the meridional ocean velocity, and is zoomed into the region near the ice-shelf base (the zoomed-in region is indicated with a black box (b)).}}
\end{center}
\label{fig:static_solo_temp_v_v}
\end{figure} 
 \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{Figures/Wind_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
%\includegraphics[width=0.99\textwidth]{Figures/ALE_z_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
\caption{ {Results of the static ice-shelf experiment using the Lagrangian ice-shelf model coupled to MOM6. The three panels show 5 year time average of the (a) melt rate, (b) top-of-ocean temperature and (c) frictional velocity, $u^{*}$, at the base of the ice shelf. Fields are only shown in regions where the ice area fraction is $\geq 0.8$.}}
\end{center}
\label{fig:static_solo_melt}
\end{figure} 
 \clearpage

  \begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Broken_Compare_melt_m_per_year_anomaly.png}
%\includegraphics[width=0.99\textwidth]{Figures/ALE_z_static_shelf_comparison_salt_layers.png}
\caption{ {(a) Snapshot of the melt rate at the base of the ice shelf 60 days after the calving event in the tabular-iceberg-calving simulation. (b) Steady state melt rate of the simulation that was spun-up from rest with the semi-circular iceberg removed..}}
\end{center}
\label{fig:broken_melt}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Collapse_ustar_iceberg.png}
%\includegraphics[width=0.99\textwidth]{Figures/ALE_z_static_shelf_comparison_salt_layers.png}
\caption{ {Snapshots of frictional velocity at the ice-shelf base in the tabular-iceberg-calving simulation. Snapshots are taken (a) 7, (b) 15, and (c) 50 days after calving.}}
\end{center}
\label{fig:ustar_calving}
\end{figure}
 \clearpage
